### 2023-10-15 chapters/discussion.tex
Add todos

% Considering VAEs and self"=supervised methods, it seems we have not yet been able to build a model that has a principled probabilistic representation of uncertainty without compromising its ability to learn representations that are useful for downstream applications.

% Different from self"=supervised methods, VAEs learn the distribution over the training data and are forced to encode all aspects important to it. 
% As we saw in \cref{chp:paper-hierarchical}, this will generally include low-level features that are important for accurate input reconstruction, but usually of lesser interest for downstream tasks.

@@

% Although the path-wise derivative has lower variance than most alternatives, such as score function estimators, a number of works have attempted to reduce its variance.
% \textcite{roeder_sticking_2017} note that the path-wise derivative can be factored into a path-wise estimator and a score function estimator and propose to ignore the score function factor to reduce gradient variance. 
% \textcite{rainforth_tighter_2019} show that this problem is even larger for the importance weighted ELBO \parencite{burda_importance_2016} and leads to diminishing returns when increasing the number of samples. 
% Rather than removing the score function factor in the estimate, \textcite{tucker_doubly_2019} propose to reparameterize it and derive low variance gradient estimators, also for importance weighted ELBO.

@@

@@

% \section{\Cref{chp:paper-hierarchical} revisited: \dots}

% \lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \parencite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
% \lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
% \lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

% \section{\Cref{chp:paper-benchmarking} revisited: Bested?}

% \lesstodo[inline]{Discuss whether variational autoencoders are viable for learning good representations for speech for downstream tasks when alternatives such as SSL method exist.}
% \lesstodo[inline]{Out-of-distribution detection on speech?}

>>>>

@@

@@

\paragraph{Giving up?}
\lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \parencite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}

\lesstodo[inline]{Out-of-distribution detection on speech?}

@@
